	\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{url}

\restylefloat{figure}
	\title{IT3708 - Exercise 4}
\author{
        Eirik Hammerstad \& Nicklas Utgaard
}
				
\date{\today}
\begin{document}
\maketitle
\section{Disclaimer}
In order to keep to our tradition of using Java in this course we decided to use it to implement our control system during this project. 
Further is it worth noting that we completed this project with three main iterations, each consisting of several subiterations. 
The first iteration was used to implement the general architecture as well as the three submodules, \textit{Search}, \textit{Retrieval}, and \textit{Stagnation}, in a very rudemental way.
This formed the basis for our second iteration where we converted the provided \textit{C} modules to Java, and introduced \textit{OOP} into these in order to fit into the overall architecture.
The last iteration of this project was used to identify improvement potential and improve upon these in the three modules implemented during the second iteration. 

\section{Part A}
	\subsection{System overview}	
		Standard architectural description + diagrams
		Change to world attenuation from 1 0 0 to 0 0 25
		

	\subsection{Inital implementation}
		Den klarer det...
		uforventet stacking av epucks funker greit. (De står bak og dytter de som er nærmere boksen) (Implemented braitenberg search, stupidConvergeAndPush and stupidStagnationAvoidance)

\section{Part B}
	\subsection{Areas of improvement}
		search: braitenburg sucks, gets stuck in corners at some times. 
		convergeAndPush: Spends a lot of time pushing when not aligned with
	the box. Move alignment from stagnation to push. 
		stagnation: Only looks directly to its side when deciding if it is going to 
	stay or not. This combined with not allways being align result in the box being counted as a neighbour in some occurences. Move alignment from stagnation to push. 
	Introduce all backwardsfacing sensors as neighboursensor, in order to also find 
	bot that are standing behind and pushing. 
		
	\subsection{Effect of improvements}
		Done
		Very well

%\pagebreak
%\tableofcontents
%\pagebreak

\end{document}